Geographically aware estimates of remotely sensed water properties for Chesapeake Bay

### 2022-09-16 manuscript/manuscript.tex
text edits

>>>>

One shortcoming of our work which may be a fruitful area of future research is the lack of realistic small-scale features evident in the physics based output of the CBOFS (Figure 4). These small-scale features such as eddies and other circulation features may be resolved with the use of convolutional neural networks (CNNs). A key difference between our approach and that of CNNs is that our approach fits each observation essentially in isolation and does not attempt to reproduce the “neighborhood” surrounding observations as is the case with CNNs (citation).

Another potential area of future research is resolving water properties at depths beyond the surface. A key challenge in this area is lack of observational data at multiple locations. Depth arrayed measurements are typically only associated with buoy deployments of which there are few in the Bay. Perhaps these can be supplemented by data from physics-based models such as CBOFS. The results of such as an effort can be regarded more so as an emulator than a standalone model.
